Structuring College Access

### 2025-04-04 index.qmd
modifying slides

@@

@@

```{r setup, echo=FALSE, results = 'asis'}

>>>>

- [College Board Student Search Service, order \#448922](./assets/images/geomarket_orders_redacted.pdf){target="_blank"}

Sorting students into colleges, perspectives from sociology

- Status attainment model [e.g., @RN915]
- Cultural capital model [e.g., @RN1228]
<!-- - "Schools as sorting machines" [@RN4873] -->
- Enrollment management behavior of colleges [e.g., @RN3519]

Sociology misses an important mechanism of social reproduction:

- Third-party vendors/products sort students on behalf of colleges
- Recommendations based on historical snapshots of student demand

We investigate "Geomarkets," an input in two College Board recruiting products

### Introduction og {.hide}

@@

# Scholarship on Enrollment Management

### __The U.S. Market for Higher Education__
#### _A National Voucher System_

- Federal government
  - Takes a "steer, don't row" approach
  - Subsidizes higher education by providing Title IV grants and loans to students
  - Department of Education regulates Title IV institutions
- Students
  - Attend college to improve career, social, and civic outcomes
  - Pay for college using: 
    - Household savings; grants and loans from federal, state, private sources
- Direct providers (Title IV institutions)
  - A mix of public, private nonprofit, for-profit providers
  - Funding follows students to whichever institution they enroll in
    - A national voucher system
  - Colleges have a financial incentive to enroll students, so competition for students

### __Student Lists are a Match-Making Intermediary__
#### _Connecting Colleges to Prospective Students_

@RN2247 on emergence of a national higher education system

- Information costs were primary barrier to efficient matches
  - Students want to attend best college, but don't know options or costs
  - Colleges want to enroll best students, but don't know who or where they are
- SAT causes "dramatic fall" in cost of "information about students" (p. 102)

In 1972, College Board began selling lists of prospects to colleges [@belkin2019-studata]

- Student list contains contract info of prospective students who meet "search filter" criteria (e.g., test score GPA) specified by the college

"Lead generation" is process of connecting merchants to potential consumers

- "List-based" lead generation
  - Based on direct mail business model, but has evolved into "database arketing"
- "Behavioral-based" targeting
  - Target users of a platform while they use that platform or a partner platform
  - Contemporary lead generation in higher education moving here

### __Enrollment Management (EM)__ {.columns-2}
#### _And the Enrollment Funnel_

::: columns

:::: {.column width=50%}

- EM profession integrates techniques from marketing and economics in order to "influence the characteristics and the size of enrolled student bodies" [@RN2771, p. xiv]
- EM office subsumes activities of recruiting, admissions, financial aid

__Interventions along the funnel__

- Convert prospects to leads 
  - Purchase student lists
- Convert leads/inquiries to applicants
  - Email, mail, school visits
- Convert applicants to admits
  - Decide who to admit
- Convert admits to enrollees
  - Financial aid offers [e.g., @RN2241]
::::

:::: {.column width=50%}
```{r, echo=FALSE, out.width="60%", fig.cap=""}
knitr::include_graphics("./assets/images/enroll_funnelv2.png")
```
::::

:::

@@

```{r setup, echo=FALSE, results = 'asis', eval = FALSE}
